---
title: "My Rmd"
output: pdf_document
---

```{r setup, include=FALSE}
require(knitr)
source("Anne_Data_1_Read.R")
source("Anne_Data_2_Clean.R")
opts_chunk$set(echo = TRUE)
```

## Setup chunck

The setup chunk above reads in, executes, but does not echo the code in the R scripts `Anne_Data_1_Read.R` and `Anne_Data_2_Read.R`.  You need those two files in the same folder as this Rmd file and as the `Annedata.xlsx` file.

## Gathering in Order to Facet_wrap

This plot gathers the tibble into a taller tibble.  All of the columns that start with "therapy" are gathered into one column called `therapy`.  Frankly, I don't know what purpose the `value = "DSAge"` parameter serves.

```{r}


DSSurvey %>% 
  gather(key = "therapy", value = "DSAge", matches("^therapy") ) %>% 
  ggplot(aes(x = visitstotal, y = income)) + 
  geom_jitter() +
  facet_wrap(~ therapy)

```

## Cleaning insurance

We were hit by the `NA` bug on this one.  We have to make sure that you account for `NA` in each of the `if_else()` statements.  This was complicated by the fact that the `NA` rules are difference for character and factor data.  To resolve that issue, all is converted to character before processing and then converted back to factor at the end.

```{r}
DSSurvey %>% 
  mutate(insurance = as.character(insurance)) %>% 
  mutate(insurance = if_else((str_detect(insurance2, "Medicare") | str_detect(insurance2, "Medicaid")) &
                          is.na(insurance),
                        "Public",
                        insurance
                        )
         ) %>% 
  mutate(insurance = if_else(!is.na(insurance2) &
                               (str_detect(insurance2, "Medicare") | str_detect(insurance2, "Medicaid")) &
                               str_detect(insurance, "Private"),
                             "Public",
                             insurance)
         ) %>% 
  mutate(insurance = if_else(!is.na(insurance2) &
                                 str_detect(insurance2, "but my DS child is only co"),
                             "Public",
                             insurance)
           ) %>% 
  mutate(insurance = as.factor(insurance)) %>% 
  select(-insurance2) -> DSSurvey
  

DSSurvey %>% 
  select(contains("insurance")) %>% 
  summary()


  
```


